A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-14 body/rbprm.tex
appendix done, missing all stats and truck
Andrea's first complete review

\section{Computing a guide path in $C_{reach}$ ($\mathcal{P}_1$) }
\label{rbprm}

We consider the issue of computing a normalized guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow SE(3)$ for the geometrical root of a multiped robot, connecting start and goal configurations. As said in the previous section, the goal is to enforce that any configuration $\mathbf{q}^0$ of the guide is truly feasible, i.e. can be mapped to a configuration in contact. We denote by $C_{contact} \subset SE(3) \times \mathbb{R}^n$ the contact submanifold of the robot.
%~ We say that a root placement $\mathbf{q}^{0}$ is \textit{truly feasible} if there exists $\mathbf{q}^{\overline{0}}$ such that 
%~ $$\mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} $$
%~ The set of all truly-feasible root placements is denoted by $C_{reach}$. By extension, a trajectory $\mathbf{q}^0(t)$ is truly feasible if $\forall t \in [0,1], \mathbf{q}^0(t) \in C_{reach}$. 
%~ We define a bijective mapping $\pi$ between $C_{reach}$ and $C_{contact}$:
%~ \begin{equation}
    %~ \pi\colon \quad \mathbf{q}^{0} \in C_{reach} \longrightarrow  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} 
    %~ \label{eq:pi}
%~ \end{equation}

We say that a root placement $\mathbf{q}^{0}$ is \textit{truly feasible} if there exists at least one bijective mapping $\pi$
such that
\begin{equation}
    \pi\colon \quad \mathbf{q}^{0} \in  SE(3) \longrightarrow  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} 
    \label{eq:pi}
\end{equation}

@@

In this Section we characterize $C_{reach}$ theoritically with a necessary and a sufficient condition for belonging to the set.
We then describe our implementation of an efficient RRT planner in $C_{reach}$.

@@

\subsubsection*{Sufficient condition for true feasibility}
%~ In building $C_{reach}^1$, we directly considered the including hull of the root body $W^{0}$, obtaining a necessary condition. 
A trivial sufficient condition for true feasibility can be constructed as a variation of $C_{reach}^1$, by replacing $W^0$ with a bounding volume $B^{max}$ encompassing the whole robot in a given pose, except for the effector surfaces to be in contact (This condition is trivial in the sense that the resulting $W$ has a zero measure. For the need of the proof, the trivial sufficient condition is enough. In practice, the construction of a non-trivial including shape $W^0$ was possible for all the robot structures we considered). We denote by $C_{reach}^\infty \subset C_{reach}$ the set of root placements corresponding to the sufficient condition.

In general, the inclusion is strict, which means that we lose the completeness of the two-stage contact planner (i.e. the planner is not able to discover a trajectory inside $C_{reach} \setminus C_{reach}^\infty$). However, the sufficient condition guarantees that any such trajectories leads to a valid sequence of contacts (i.e. $\pi$ is defined).

@@

However between $W^0$ and $B^{max}$, a trade-off can be found between a necessary and a sufficient condition. We define $W^0_s$ as the volume $W^0$ subject to a scaling transformation by a factor $s \in \mathbb{R}^+$. 
%
We then consider the spaces $C_{reach}^s$
 \begin{equation}
C_{reach}^s = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \wedge W^0_s(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \wedge & A_{trunk}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%
The higher $s$ is, the closer this "reachability condition" is to being sufficient, and if $s=1$, the planner is complete. The parametrization of $s$ allows to find a trade-off between these two desirable properties.
As an example, Figure~\ref{fig:hyq_roms} presents the volumes $W$ computed for the HyQ robot.
In Appendix~\ref{app:rom}, we give a generic method to compute these volumes, with the example of HRP-2.
%~ Section~\ref{sec:results} shows that in practice, it is easy to adjust $s$ to keep most of the interesting guides without introducing incorrect guides.

@@

However, to improve the sampling efficiency while remaining probabilistically complete, we bias the sampling process to generate near obstacle configurations, similarly to~\cite{Amato98choosinggood}.
First, a configuration is set to a random point on the surface of one randomly chosen obstacle. The root location is then translated and rotated randomly until the reachability condition is satisfied.
Our current implementation of these modifications is based on the Bi-RRT planner provided by the hpp software.

Thanks to this small set of modifications, the high dimensional truly feasible path planning problem is reduced to a standard geometry and collision checking problem, in a much lower dimension (6 for Hyq, 8 for HRP-2 that has a flexible torso). In so doing we make the problem tractable for sampling based approaches, with extremely efficient computation times.

>>>>

% !TEX root =  ../main.tex
\section{Computing a guide path in $C_{reach}$ ($\mathcal{P}_1$) }
\label{rbprm}

We consider the issue of computing a normalized guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow SE(3)$ for the geometrical \adnote{why the root is geometrical? Isn't the path to be geometrical?} root of a multiped robot, connecting \adnote{user-defined} start and goal configurations. As said in the previous section, the goal is to enforce that any configuration $\mathbf{q}^0$ of the guide is \replaced{geometrically}{truly} feasible, i.e. can be mapped to a configuration in contact. We denote by $C_{contact} \subset SE(3) \times \mathbb{R}^n$ the contact submanifold of the robot\added{, that is the set of configurations in which the robot is in contact with the environment}.
%~ We say that a root placement $\mathbf{q}^{0}$ is \textit{truly feasible} if there exists $\mathbf{q}^{\overline{0}}$ such that 
%~ $$\mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} $$
%~ The set of all truly-feasible root placements is denoted by $C_{reach}$. By extension, a trajectory $\mathbf{q}^0(t)$ is truly feasible if $\forall t \in [0,1], \mathbf{q}^0(t) \in C_{reach}$. 
%~ We define a bijective mapping $\pi$ between $C_{reach}$ and $C_{contact}$:
%~ \begin{equation}
    %~ \pi\colon \quad \mathbf{q}^{0} \in C_{reach} \longrightarrow  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} 
    %~ \label{eq:pi}
%~ \end{equation}

We say that a root placement $\mathbf{q}^{0}$ is \textit{\replaced[remark={I don't replace 'truly feasible' with 'geometrically feasible' from now on because I don't know whether you like it}]{geometrically}{truly} feasible} if there exists at least one bijective mapping $\pi$
such that
\begin{equation}
    \pi\colon \quad \mathbf{q}^{0} \in  SE(3) \longrightarrow  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} 
    \label{eq:pi}
\end{equation}

@@

In this Section we characterize $C_{reach}$ theoretically with a necessary and a sufficient condition for belonging to the set.
We then describe our implementation of an efficient RRT planner in $C_{reach}$.

@@

\subsubsection*{\replaced[remark={for coherence with previous subsection title}]{True feasibility: sufficient condition}{Sufficient condition for true feasibility}}
%~ In building $C_{reach}^1$, we directly considered the including hull of the root body $W^{0}$, obtaining a necessary condition. 
A trivial sufficient condition for true feasibility can be constructed as a variation of $C_{reach}^1$, by replacing $W^0$ with a bounding volume $B^{max}$ encompassing the whole robot in a given pose, except for the effector surfaces to be in contact (This condition is trivial in the sense that the resulting $W$ has a zero measure. For the need of the proof, the trivial sufficient condition is enough. In practice, the construction of a non-trivial including shape $W^0$ was possible for all the robot structures we considered). \adnote{Isn't this parenthesis a bit too long?} We denote by \mbox{$C_{reach}^\infty \subset C_{reach}$} the set of root placements corresponding to the sufficient condition.

In general, the inclusion is strict, which means that we lose the completeness of the two-stage contact planner (i.e. the planner is not able to discover a trajectory inside \mbox{$C_{reach} \setminus C_{reach}^\infty$}). However, the sufficient condition guarantees that any such trajectories leads to a valid sequence of contacts (i.e. $\pi$ is defined).

@@

However, between $W^0$ and $B^{max}$, a trade-off can be found between a necessary and a sufficient condition. We define $W^0_s$ as the volume $W^0$ subject to a scaling transformation by a factor $s \in \mathbb{R}^+$. 
%
We then consider the spaces $C_{reach}^s$
 \begin{equation}
C_{reach}^s = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \wedge W^0_s(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \wedge & A_{trunk}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%
The higher $s$, the closer this ``reachability condition'' is to being sufficient, and if $s=1$, the planner is complete. The parametrization of $s$ allows to find a trade-off between these two desirable properties.
As an example, Figure~\ref{fig:hyq_roms} presents the volumes $W$ computed for the HyQ robot.
In Appendix~\ref{app:rom}, we give a generic method to compute these volumes, with the example of HRP-2.
%~ Section~\ref{sec:results} shows that in practice, it is easy to adjust $s$ to keep most of the interesting guides without introducing incorrect guides.

@@

However, to improve the sampling efficiency while remaining probabilistically complete, we bias the sampling process to generate near obstacle configurations, similarly to~\cite{Amato98choosinggood}.
First, a configuration is set to a random point on the surface of one randomly chosen obstacle. The root location is then translated and rotated randomly until the reachability condition is satisfied.
Our current implementation of these modifications is based on the Bi-RRT planner provided by the HPP software.

Thanks to this small set of modifications, the high dimensional truly feasible path planning problem is reduced to a standard geometry and collision checking problem, in a much lower dimension (6 for Hyq, 8 for HRP-2 that has \replaced{joints in the}{a flexible} torso). \replaced{By doing do}{In so doing} we make the problem tractable for sampling-based approaches, with extremely efficient computation times.

### 2015-12-14 body/results.tex
Andrea's first complete review

 \section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large vartiety of environments: the humanoid HRP-2 and the quadriped Hyq.
For each scenario we indicate the heuristics chosen. We also provide a performance analysis, that shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario.
We also demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dextrous manipulation.

In our ISRR conference paper~\citep{tonneauisrr15}, additional results are demonstrated with various virtual avatars (Figure~\ref{fig:robots_old}).
In this extension we choose to focus on results obtained with actual robots. We invite the interested reader to watch the ISRR video\endnote{https://www.youtube.com/watch?v=LmLAHgGQJGA}, and 
to refer to the previous paper for a discussion on these results.

@@

The goal is to cross a set of stairs of a height of 20 cm. This height requires HRP-2 to use a ramp to be able to perform the task.

\noindent\textbf{Contacts involved:} Both feet and right arm.

\noindent\textbf{Heuristics:} The extended manipulability $h_w$ is chosen for the feet; $h_{EFORT}$ is chosen for the right arm.
Regarding equilibrium, the video demonstrates two sequences computed for two different treshold values of $b_0$: $0$ and $2$ (Figure~\ref{fig:stair_robust}).

\noindent\textbf{Observations:}
This scenario illustrates best the importance of the equilibrium robustness criterion.
With a robust approach, more states are required to reach the last step (15 against 13 in average).
However, when the last step is reached by both feet, in the non robust case, the contacts are extremely close to 
the cone limits, and we believe this can be seen visually (Figure~\ref{fig:stair_comp}).

@@

\subsubsection{HRP-2 -- Standing up (Figure~\ref{fig:standing}):}
From a bent configuration, a standing up motion is computed in a cluttered environment.
The resulting motion involves using a wall as support, and crossing a 25 cm high stair.

@@

\noindent\textbf{Heuristics:} $h_w$ is used for the feet, $h_{EFORT}$ is used for the hands.

\noindent\textbf{Observations:} The scenario illustrates well the acyclic aspect of the planning. For instance, in the 4 first frames of Figure~\ref{fig:standing}, we can see that the right foot
is moved twice, with the left foot in between, before the configuration allows HRP-2 to move its hand.
Because the contacts are tried in a FIFO manner, the fact that the output contact sequence is acyclic shows that a cyclic approach (with a finite state machine for instance) is not sufficient
for the computed trajectory. The reason for this is not reachability, but equilibrium. The planning is slower than for the stair scenario (because the contact generation fails more),
though it remains compatible with interactive performances.

\subsubsection{HRP-2 -- Truck egress (Figure~\ref{fig:TODO}):}
HRP-2 stands half sitted in a truck, and is required to exit through the front window.

@@

\noindent\textbf{Heuristics:} $h_w$ is used for the feet, $h_{EFORT}$ is used for the hands.

\noindent\textbf{Observations:} This scenario demonstrates the ability of the planner to compute a path in an extremely constrained environment. In this case,
the scenario is not always real time (TODO or is it ?): while the planner is often able to compute a guide path rapidly, in the worst case up to one minute can be spent
in the planning.

\subsubsection{HyQ -- Darpa style rubble (Figure~\ref{fig:darpa})}
The quadruped robot is given the task to cross a rubble composed of bricks rotated at different angles and directions.

@@

\noindent\textbf{Heuristics:} $h_w$ is used for the all legs. The robustness treshold $b_0$ is set to $20$.

\noindent\textbf{Observations:} In this context, setting up a really important minimum value for $b_0$ is possible due to the high
stability of the HyQ robot, and results in more contact switches, in exchange for safety. The path planning time is higher than for the previous HRP-2 robots due to the constraint that the 4 reachable workspace of all legs must
collide with the environment at all times. Again, the computed time remains however interactive.

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:hyq_bridge} and~\ref{fig:hyq_obs}):}
In this long scene, HyQ is first required to cross a 55 cm large hole; then, to cross a narrow "bridge", only large of 25 cm,
while maintaining equilibrium.

@@

\noindent\textbf{Heuristics:} $h_w$ is used for the all legs. The robustness treshold $b_0$ is set to $4$.

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is the harder to compute for our planner.
While finding a guide path above the hole is easy for the planner, finding a relevant sequence of contacts that remain in equilibrium is not trivial.
Secondly, the narrow bridge is hard both for the planner and the contact generator: To make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the right angle.
This can be seen in Figure (TODO), where several feet repositionning are required to cross both obstacles (although the video shows this best).
The planner however suceeds in finding a feasible sequence in the end, again with interactive computation times.

\subsubsection{HRP-2 -- Path replanning(Figure~\ref{fig:replanning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications involve replanning.

@@

\noindent\textbf{Contacts involved:} Both feet and the right arm.

\noindent\textbf{Heuristics:} $h_w$ is used for the all legs. $h_{EFORT}$ is used for the right arm. The robustness treshold is set to $2$.

\noindent\textbf{Observations:} This scenario is designed to illustrate concretely the computation times of the planner.
In the video, the footsteps indicating the contact sequence appear at the average speed of their computation (including the guide path planning).

\subsubsection{3-fingered hand -- Manipulation of a pen (Figure~\ref{fig:penrot}):}
This scenario is proposed to illustrate the genericity of our approach: we consider a manipulation task for a robotic hand and use
our contact planner to compute a guide trajectory for the fingers, considered as effectors (Figure~\ref{fig:penrot}).
Although we do not address the hard issue of accounting for rolling motions, the planner is able to compute the shown sequences, this in less than 5 seconds.

@@

\noindent\textbf{Heuristics:} $h_{EFORT}$ is used for the all fingers.

@@

In most scenarios, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. 
Considering the repartition of the computation time, it appears that the majority of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state of the art IK solutions, we believe there is room
for improving the performances of the algorithm.

@@

We observe that, as expected, our planner does not succeed systematically, because of the approximations made in the implementation
of our theoritical formulation. 
From a pragmatic point of view, regarding the computation times, we claim that our approach is the best current compromise between completeness and efficiency:
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to replan a new contact sequence also rapidly with 
a reasonable chance of success.

>>>>

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ~\cite{Semini}.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario.
Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dextrous manipulation.

In our previous work~\citep{tonneauisrr15} additional results are demonstrated with various virtual avatars (Fig.~\ref{fig:robots_old}).
In this extension we choose to focus on \deleted{results obtained with} actual robots. We invite the interested reader to watch the ISRR video\endnote{https://www.youtube.com/watch?v=LmLAHgGQJGA}, and 
to refer to the previous paper for a discussion on these results.

@@

The goal is to climb three 20-cm high steps. This height requires HRP-2 to use a ramp to \deleted{be able to} perform the task.

\noindent\textbf{Contacts involved:} \deleted{Both} Feet and right arm.

\noindent\textbf{Heuristics:} The extended manipulability $h_w$ is chosen for the feet; $h_{EFORT}$ is chosen for the right arm.
Regarding equilibrium, the video demonstrates two sequences computed for two different threshold values of $b_0$: $0$ and $2$ (Fig.~\ref{fig:stair_robust}).

\noindent\textbf{Observations:}
This scenario illustrates best the importance of the equilibrium-robustness criterion.
With a robust approach, more states are required to reach the last step (15 \replaced{rather than}{against} 13 in average).
However, when the last step is reached by both feet, in the nonrobust case the contacts are extremely close to 
the cone limits\deleted{, and we believe this can be seen visually} (Fig.~\ref{fig:stair_comp}).

@@

\subsubsection{HRP-2 -- Standing up (Fig.~\ref{fig:standing}):}
From a bent configuration, a standing-up motion is computed in a cluttered environment.
The resulting motion involves using a wall as support, and climbing a 25-cm high step.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for the feet, $h_{EFORT}$ \deleted{is used} for the hands.

\noindent\textbf{Observations:} The scenario illustrates well the acyclic aspect of the planning. For instance, in the four first frames of Fig.~\ref{fig:standing}, we can see that the right foot
is moved twice, with the left foot in between, before the configuration allows HRP-2 to move its hand.
Because the contacts are tried in a FIFO manner, the fact that the output contact sequence is acyclic shows that a cyclic approach (with a finite state machine for instance) is not sufficient
for the computed path. The reason for this is not reachability, but equilibrium. The planning is slower than for the stair scenario (because the contact generation fails more),
though it remains compatible with interactive performances. \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

\subsubsection{HRP-2 -- Truck egress (Fig.~\ref{fig:TODO}):}
HRP-2 stands half seated in a truck, and \replaced{is required to}{it must} \replaced{get out}{exit} through the front window.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for the feet, $h_{EFORT}$ \deleted{is used} for the hands.

\noindent\textbf{Observations:} This scenario demonstrates the ability of the planner to compute a path in an extremely-constrained environment. In this case,
the scenario is not always real time (TODO or is it ?): while the planner is often able to compute a guide path rapidly, in the worst case up to one minute can be spent
in the planning.

\subsubsection{HyQ -- Darpa-style rubble (Fig.~\ref{fig:darpa})}
The quadruped robot is given the task to cross a rubble composed of bricks rotated at different angles and directions.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for all legs. The robustness threshold $b_0$ is set to $20$.

\noindent\textbf{Observations:} In this context, setting up a really important minimum value for $b_0$ is possible due to the high
stability of the HyQ robot, and results in more contact switches, in exchange for safety. The path-planning time is higher than for the previous HRP-2 robots due to the constraint that the 4 reachable workspace of all legs must
collide with the environment at all times. \adnote{Why do not relax this constraint and require only 3 legs?} Again, the computed time remains however interactive.

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:hyq_bridge} and~\ref{fig:hyq_obs}):}
In this long scene, HyQ is first required to cross a 55-cm large hole; then, to cross a narrow "bridge",  only 25-cm large\deleted{,
while maintaining equilibrium}.

@@

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for all legs. The robustness threshold $b_0$ is set to $4$.

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is the hardest \deleted{to compute} for our planner.
While finding a guide path above the hole is easy for the planner, finding a \deleted{relevant} sequence of contacts that \replaced{allows for}{remain in} equilibrium is not trivial.
Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the right angle.
This can be seen in Fig.~(TODO), where several feet \replaced{rearrangements}{repositioning} are required to cross both obstacles (although the video shows this best).
The planner however succeeds in finding a feasible sequence in the end, again with interactive computation times.

\subsubsection{HRP-2 -- Path replanning(Figure~\ref{fig:replanning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications \replaced{demands}{involve} replanning.

@@

\noindent\textbf{Contacts involved:} \replaced{F}{Both f}eet and the right arm.

\noindent\textbf{Heuristics:} $h_w$ \deleted{is used} for all legs. $h_{EFORT}$ \deleted{is used} for the right arm. The robustness threshold is set to $2$.

\noindent\textbf{Observations:} This scenario is designed to illustrate concretely the computation times of the planner.
In the video, the footsteps indicating the contact sequence appear at the average speed of their computation (including the guide-path planning).

\subsubsection{3-fingered hand -- Manipulation of a pen (Fig.~\ref{fig:penrot}):}
This scenario is proposed to illustrate the generality of our approach: we consider a manipulation task for a robotic hand and use
our contact planner to compute a guide trajectory for the fingers, considered as effectors (Fig.~\ref{fig:penrot}).
Although we do not address the hard issue of accounting for rolling motions, the planner is able to compute the shown sequences\deleted{, this} in less than 5 seconds.

@@

\noindent\textbf{Heuristics:} $h_{EFORT}$ \deleted{is used} for all fingers.

@@

In most scenarios, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. 
Considering the repartition of the computation time, it appears that \replaced{most}{the majority} of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state-of-the-art IK solutions, we believe there is room
for improving the performances of the algorithm.

@@

We observe that, as expected, our planner does not succeed systematically, because of the approximations made in the implementation
of our theoretical formulation. 
From a pragmatic point of view, regarding the computation times, we claim that our approach is the best current compromise between completeness and efficiency:
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to rapidly replan a new contact sequence with 
a reasonable chance of success.
